Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
last changes

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and therefore ovule fertilization. An increasing number of visits generally correlates with higher chances of fertilization (Refs). However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs). Moreover, other less studies issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008.

@@

The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008). Invasive species are supposed to have greater negative effect than native ones @arceo2016. Although when non-natives species don´t have greater negative effect we still don´t know why. For this reason, this ecological question is non a native non native one is a trait based issue that is still to be solved. Moreover, the quantity of pollen that integrates in the network can be quite variable ranging from low quatities @bartomeus2008 to intermediate (ref) to high (ref). Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs). There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect. Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect. Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.

@@

>>>>

In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003. This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014. Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and hence ovule fertilization. An increasing number of visits generally correlates with higher chances of fertilization (Refs). However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs). Moreover, other less study
issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 (More refs).

@@

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 (More refs).

Invasive species are supposed to have greater negative effect than native ones @arceo2016. Although when non-natives species don´t have greater negative effect we still don´t know why. For this reason, this ecological question is non a native non native one is a trait based issue that is still to be solved. Moreover, the quantity of pollen that integrates in the network can be quite variable ranging from low quatities @bartomeus2008 to intermediate (ref) to high (ref). Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs). There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect. Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect. Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.

@@

Sell well our work: We are the first empirical experiment testig the effect of heterospecific pollen with phylogenetic distance

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
last changes

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and therefore
ovule fertilization. An increasing number of visits generally correlates
with higher chances of fertilization (Refs). However this is not always
the case, among these possible flower visitors we find also nectar
robbers and pollen thiefs (Refs) and the quality of pollen that is
deposited on the stigma is also highly relevant to the pollination
succes (Refs). Moreover, other less studies issues in the pollination
process are conspecific pollen loss and the arrival of foreign pollen
which can have important detrimental effects for the species fitness
Morales and Traveset (2008).

@@

The effect of heterospecific pollen has been widely studied (Morales \&
Traveset 2008). Invasive species are supposed to have greater negative
effect than native ones Arceo-Gómez and Ashman (2016). Although when
non-natives species don´t have greater negative effect we still don´t
know why. For this reason, this ecological question is non a native non
native one is a trait based issue that is still to be solved. Moreover,
the quantity of pollen that integrates in the network can be quite
variable ranging from low quatities Bartomeus et al. (2008) to
intermediate (ref) to high (ref). Moreover, closely related species are
supposed to reduce fitness in greater effect but the evidence is scarce
and based on independent studies with different methodologies
(Arceo-gomez \& Ashman 2016) or studies that just check it with a pair
of species that are highly related with the aim to understand
hybridization costs (refs). There is a need to deepen into how
relatednes is involve in the costs of heterospecific pollen effect.
Furthermore, following the conceptual trait framework of Ashman and
Arceo-Gomez on heterospecific pollen there are good theoretical basis
for trait effect. Notwithstanding, non empirical work has tested how
really these traits are involved in heterospecific pollen effect.

>>>>

In natural systems plant species normally coexist and share their floral
visitors with other species Bascompte et al. (2003). This pollinator
sharing from the plant perspective at the pre-pollination stage can be
negative due to competition Pauw (2013) or positive due to facilitation
Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
flower, pollen deposition on the stigma can take place and hence ovule
fertilization. An increasing number of visits generally correlates with
higher chances of fertilization (Refs). However this is not always the
case, among these possible flower visitors we find also nectar robbers
and pollen thiefs (Refs) and the quality of pollen that is deposited on
the stigma is also highly relevant to the pollination succes (Refs).
Moreover, other less studies issues in the pollination process are
conspecific pollen loss and the arrival of foreign pollen which can have
important detrimental effects for the species fitness Morales and
Traveset (2008) (More refs).

@@

Recent important studies have advanced in the ecological importance of
heterospecific pollen effect Morales and Traveset (2008) (More refs).

Invasive species are supposed to have greater negative effect than
native ones Arceo-Gómez and Ashman (2016). Although when non-natives
species don´t have greater negative effect we still don´t know why. For
this reason, this ecological question is non a native non native one is
a trait based issue that is still to be solved. Moreover, the quantity
of pollen that integrates in the network can be quite variable ranging
from low quatities Bartomeus et al. (2008) to intermediate (ref) to high
(ref). Moreover, closely related species are supposed to reduce fitness
in greater effect but the evidence is scarce and based on independent
studies with different methodologies (Arceo-gomez \& Ashman 2016) or
studies that just check it with a pair of species that are highly
related with the aim to understand hybridization costs (refs). There is
a need to deepen into how relatednes is involve in the costs of
heterospecific pollen effect. Furthermore, following the conceptual
trait framework of Ashman and Arceo-Gomez on heterospecific pollen there
are good theoretical basis for trait effect. Notwithstanding, non
empirical work has tested how really these traits are involved in
heterospecific pollen effect.
